Heatmaps of pleiotropy test statistics

### 2019-07-22 analysis/paper/heatmaps-pleiotropy-statistics-subset-locals.Rmd
created a Rmd file to outline the ms

```{r make_nonlocal_annot-2}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_scols-2}
scols <- 1L + (rownames(pm) %in% local_annot2$symbol)
scols2 <- rownames(pm) %in% (med_tib %>% filter(local_symbol == keller_mediator, lod_diff > 1.5))$nonlocal_symbol
```

@@

```{r heat8-2}
ord <- pm %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(pm)) %>%
  order.dendrogram()
## order pm (and sidecols!) according to dendrogram from above
```

```{r make_scols-extra-2}
scols_extra <- purrr::map(.x = local_annot2$symbol, 
                                       .f = function(x) {rownames(pm) %in% (med_tib %>% filter(local_symbol == x, lod_diff > 1.5))$nonlocal_symbol}
) %>% 
  bind_cols() %>%
  (function(x){colnames(x) <- local_annot2$symbol; x}) %>%
  mutate(local = scols)
```

@@

```{r count_med}
n_med_tr <- 4
(n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)
  )
scols <- scols_extra %>%
  dplyr::select(local, n_med_per_local$local_symbol)
```

```{r heat9-2}
pm[ord, ord] %>%
  apply(FUN = hotspots::trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE, 
            Colv = FALSE, 
            cexRow = 0.2, 
            cexCol = 0.2, 
            symm = TRUE, 
            row_side_colors = scols[ord, ],
            limits = c(0, 5)
            )
```

>>>>

```{r make_nonlocal_annot-2}
nonlocal_annot <- dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  inner_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= 7.18) %>%
  mutate(local_tx = chr == hot_chr) %>%
  filter(!local_tx) %>% 
  filter(!is.na(hotspot))
```

@@

```{r make_scols-2}
scols1 <- 1L + (rownames(pm) %in% local_annot2$symbol)
scols2 <- rownames(pm) %in% (med_tib %>% filter(local_symbol == keller_mediator, lod_diff > 1.5))$nonlocal_symbol
```

@@

```{r heat8-2}
# order the nonlocal traits first
## indicator for being a nonlocal trait
indic_nonlocal <- rownames(pm) %in% nonlocal_annot$symbol
# define ord_nonlocal
ord_nonlocal <- pm[indic_nonlocal, indic_nonlocal] %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(pm[indic_nonlocal, indic_nonlocal])) %>%
  order.dendrogram()
rn_nonlocal <- rownames(pm[indic_nonlocal, indic_nonlocal][ord_nonlocal, ord_nonlocal])
# define ord_local
ord_local<- pm[!indic_nonlocal, !indic_nonlocal] %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(pm[!indic_nonlocal, !indic_nonlocal])) %>%
  order.dendrogram()
rn_local <- rownames(pm[!indic_nonlocal, !indic_nonlocal][ord_local, ord_local])
rn <- c(rn_nonlocal, rn_local)
```

```{r make_scols-extra-2}
scols_extra <- purrr::map(.x = local_annot2$symbol, 
                          .f = function(x) {rownames(pm) %in% (med_tib %>% filter(local_symbol == x, lod_diff > 1.5))$nonlocal_symbol}
) %>% 
  bind_cols() %>%
  (function(x){colnames(x) <- local_annot2$symbol; x}) %>%
  mutate(local = scols1)
```

@@

```{r count_med}
n_med_tr <- 4 # arbitrary threshold
(n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)
  )
scols_pre <- scols_extra %>%
  dplyr::select(n_med_per_local$local_symbol)
# get ordering for columns of scols_pre
col_order <- scols_pre %>%
  t() %>%
  dist() %>%
  hclust() %>%
  as.dendrogram() %>%
  dendextend::seriate_dendrogram(dist(t(scols_pre))) %>%
  order.dendrogram()
scols <- scols_pre[ , col_order] %>%
  mutate(local = scols1)
```

```{r heat9-2}
ord <- match(rn, rownames(pm))

pm[ord, ord] %>%
  apply(FUN = hotspots::trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE, 
            Colv = FALSE, 
            cexRow = 0.2, 
            cexCol = 0.2, 
            symm = TRUE, 
            row_side_colors = scols[ord, ],
            col_side_colors = scols1[ord],
            limits = c(0, 5)
            )
```
